---
title: "TSQCA Tutorial (English)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TSQCA Tutorial (English)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

Threshold-Sweep QCA (TS-QCA) is a framework for systematically exploring how different threshold settings affect the results of crisp-set Qualitative Comparative Analysis (QCA).  
In crisp-set QCA, the researcher must choose thresholds to binarize:

- the outcome **Y**, and
- the conditions **X**.

Small changes in these thresholds may lead to substantial differences in truth tables and minimized solutions.

TS-QCA provides:

- a **systematic** way to vary thresholds,
- a **transparent** way to evaluate sensitivity,
- and a **reproducible** workflow for robustness assessment.

The `TSQCA` package implements four sweep methods:

| Method | What varies | What stays fixed | Purpose |
|--------|-------------|------------------|----------|
| **CTS–QCA** | One X threshold | Y + other Xs | Evaluate influence of a single condition |
| **MCTS–QCA** | Multiple X thresholds | Y | Explore combinations of X thresholds |
| **OTS–QCA** | Y threshold | All Xs | Assess robustness to Y calibration |
| **DTS–QCA** | X and Y thresholds | None | Full 2D sensitivity analysis |

---

# Data Requirements

TS-QCA assumes:

- Data are calibrated (e.g., 0–10 scale or fuzzy-set values).
- Thresholds are numeric (integer or real).
- Missing values should be handled before running sweeps.

Example dataset structure:
```{r}
library(TSQCA)
data("sample_data")
dat <- sample_data
str(dat)
```

Define outcome and conditions:
```{r}
Yvar  <- "Y"
Xvars <- c("X1", "X2", "X3")
```

---

# CTS–QCA: Single-Condition Sweep (`ctSweepS`)

CTS–QCA varies the threshold for **one X condition**, keeping the others fixed.
```{r, error=TRUE}
sweep_var   <- "X3"   # 閾値を変化させる対象の条件（X）
sweep_range <- 6:9    # 試す閾値候補

thrY         <- 7     # Y の閾値（固定）
thrX_default <- 7     # その他 X の閾値（固定）

res_cts <- ctSweepS(
  dat            = dat,
  Yvar           = Yvar,
  Xvars          = Xvars,
  sweep_var      = sweep_var,
  sweep_range    = sweep_range,
  thrY           = thrY,
  thrX_default   = thrX_default,
  return_details = FALSE
)

head(res_cts)
```

---

# MCTS–QCA: Multiple X Sweep (`ctSweepM`)

MCTS–QCA evaluates all combinations of thresholds for multiple X conditions.
```{r, error=TRUE}
sweep_list <- list(
  X1 = 6:8,
  X2 = 6:8,
  X3 = 6:8
)

res_mcts <- ctSweepM(
  dat            = dat,
  Yvar           = Yvar,
  Xvars          = Xvars,
  sweep_list     = sweep_list,
  thrY           = 7,
  return_details = FALSE
)

head(res_mcts)
```

---

# OTS–QCA: Outcome Sweep (`otSweep`)

OTS–QCA varies only the threshold of **Y**, keeping X thresholds fixed.
```{r}
thrX <- c(X1 = 7, X2 = 7, X3 = 7)

res_ots <- otSweep(
  dat            = dat,
  Yvar           = Yvar,
  Xvars          = Xvars,
  sweep_range    = 6:9,
  thrX           = thrX,
  return_details = FALSE
)

head(res_ots)
```

---

# DTS–QCA: Two-Dimensional Sweep (`dtSweep`)

DTS–QCA varies both **X thresholds** and **Y thresholds**, creating a full 2D grid.
```{r}
sweep_list_X <- list(
  X1 = 6:8,
  X2 = 6:8,
  X3 = 6:8
)

sweep_range_Y <- 6:8

res_dts <- dtSweep(
  dat            = dat,
  Yvar           = Yvar,
  Xvars          = Xvars,
  sweep_list_X   = sweep_list_X,
  sweep_range_Y  = sweep_range_Y,
  return_details = FALSE
)

head(res_dts)
```

---

# Understanding the Output

Each sweep result contains:

- threshold values tested,
- minimized solution expression,
- solution consistency (`inclS`),
- solution coverage (`covS`).

General guidance:

- **Consistency ≥ 0.8** is typically required for sufficiency.
- **Coverage** indicates empirical relevance; higher is better.
- A solution sensitive to small threshold changes suggests low robustness.

---

# Conclusion

TSQCA provides a structured and reproducible way to evaluate  
how threshold choices influence QCA results.

Using CTS, MCTS, OTS, and DTS sweeps, researchers can:

- assess robustness,
- identify stable causal patterns,
- detect threshold-sensitive relationships,
- and strengthen QCA validity.


## References

For more information on TS-QCA methodology, see:

- Ragin, C. C. (2008). *Redesigning Social Inquiry: Fuzzy Sets and Beyond*. University of Chicago Press. DOI: [10.7208/chicago/9780226702797.001.0001](https://doi.org/10.7208/chicago/9780226702797.001.0001)
- Duşa, A. (2019). *QCA with R: A Comprehensive Resource*. Springer. DOI: [10.1007/978-3-319-75668-4](https://doi.org/10.1007/978-3-319-75668-4)
- Oana, I.-E., & Schneider, C. Q. (2024). A Robustness Test Protocol for Applied QCA: Theory and R Software Application. *Sociological Methods & Research*, 53(1), 57–88. DOI: [10.1177/00491241211036158](https://doi.org/10.1177/00491241211036158)



# Session Info
```{r}
sessionInfo()
```