---
title: "TSQCA Tutorial (English)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TSQCA Tutorial (English)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

Threshold-Sweep QCA (TS-QCA) is a framework for systematically exploring how different threshold settings affect the results of crisp-set Qualitative Comparative Analysis (QCA).  
In crisp-set QCA, the researcher must choose thresholds to binarize:

- the outcome **Y**, and
- the conditions **X**.

Small changes in these thresholds may lead to substantial differences in truth tables and minimized solutions.

TS-QCA provides:

- a **systematic** way to vary thresholds,
- a **transparent** way to evaluate sensitivity,
- and a **reproducible** workflow for robustness assessment.

The `TSQCA` package implements four sweep methods:

| Method | What varies | What stays fixed | Purpose |
|--------|-------------|------------------|----------|
| **CTS–QCA** | One X threshold | Y + other Xs | Evaluate influence of a single condition |
| **MCTS–QCA** | Multiple X thresholds | Y | Explore combinations of X thresholds |
| **OTS–QCA** | Y threshold | All Xs | Assess robustness to Y calibration |
| **DTS–QCA** | X and Y thresholds | None | Full 2D sensitivity analysis |

> **Scope:** This package focuses on **sufficiency analysis**—identifying condition combinations that are sufficient for an outcome. Necessity analysis (whether a condition is required for an outcome) involves different logical structures and evaluation metrics, and is planned for future versions.

---

# Data Requirements

TS-QCA assumes:

- Data are calibrated (e.g., 0–10 scale or fuzzy-set values).
- Thresholds are numeric (integer or real).
- Missing values should be handled before running sweeps.

Example dataset structure:
```{r}
library(TSQCA)
data("sample_data")
dat <- sample_data
str(dat)
```

Define outcome and conditions:
```{r}
outcome  <- "Y"
conditions <- c("X1", "X2", "X3")
```

---

# Working with Mixed Data Types

## Handling Binary and Continuous Variables

In real-world social science research, datasets often contain **both binary variables** (e.g., gender, yes/no responses) **and continuous variables** (e.g., sales, satisfaction scores). When using TSQCA with such mixed data, special attention is required.

### Key Principles

1. **Do NOT sweep binary variables** — they are already binarized (0/1)
2. **Use threshold = 1 for binary variables** to preserve their original values
3. **Explicitly specify thresholds** for each variable in `sweep_list`

### Why Threshold = 1 for Binary Variables?

The internal `qca_bin()` function uses the rule `x >= thr` for binarization:

- If `x = 0`: `0 >= 1` → FALSE → **0** (preserved)
- If `x = 1`: `1 >= 1` → TRUE → **1** (preserved)

This ensures that binary variables remain unchanged during the binarization process.

### Practical Example: Mixed Data

Suppose your dataset has:

- **X1**: Gender (0 = Male, 1 = Female) — binary variable
- **X2**: Product Quality Score (0-10) — continuous variable
- **X3**: Store Atmosphere Score (0-10) — continuous variable

When using `ctSweepM()`:

```{r, eval=FALSE}
# CORRECT: Specify threshold explicitly for each variable
sweep_list <- list(
  X1 = 1,      # Binary variable: use threshold 1
  X2 = 6:8,    # Continuous: sweep thresholds
  X3 = 6:8     # Continuous: sweep thresholds
)

res_mixed <- ctSweepM(
  dat            = dat,
  outcome        = "Y",
  conditions     = c("X1", "X2", "X3"),
  sweep_list     = sweep_list,
  thrY           = 7,
  dir.exp        = 1
)
```

This explores 1 × 3 × 3 = **9 threshold combinations**, treating X1 as a fixed binary condition while sweeping X2 and X3.

### Common Mistake

```{r, eval=FALSE}
# WRONG: Using sweep range for binary variables
sweep_list <- list(
  X1 = 6:8,    # All values become 0 (since 0 < 6 and 1 < 6)
  X2 = 6:8,
  X3 = 6:8
)
```

If you accidentally specify `X1 = 6:8`, both 0 and 1 will fail the `>= 6` condition, making all X1 values become 0. This destroys the information in your binary variable.

### Best Practice

Always examine your data structure before setting up threshold sweeps:

```{r, eval=FALSE}
# Check variable ranges
summary(dat[, c("X1", "X2", "X3")])

# Identify binary variables (only 0 and 1)
sapply(dat[, c("X1", "X2", "X3")], function(x) {
  unique_vals <- sort(unique(x))
  if (length(unique_vals) == 2 && all(unique_vals == c(0, 1))) {
    "Binary (use threshold = 1)"
  } else {
    paste("Continuous (range:", min(x), "-", max(x), ")")
  }
})
```

---

# CTS–QCA: Single-Condition Sweep (`ctSweepS`)

CTS–QCA varies the threshold for **one X condition**, keeping the others fixed.
```{r, error=TRUE}
sweep_var   <- "X3"   # Condition (X) whose threshold is swept
sweep_range <- 6:9    # Candidate threshold values to evaluate

thrY         <- 7     # Outcome (Y) threshold (fixed)
thrX_default <- 7     # Threshold for other X conditions (fixed)

res_cts <- ctSweepS(
  dat            = dat,
  outcome        = "Y",
  conditions     = c("X1", "X2", "X3"),
  sweep_var      = sweep_var,
  sweep_range    = sweep_range,
  thrY           = thrY,
  thrX_default   = thrX_default,
  dir.exp        = 1,
  return_details = TRUE
)

head(res_cts$summary)
```

---

# MCTS–QCA: Multiple X Sweep (`ctSweepM`)

MCTS–QCA evaluates all combinations of thresholds for multiple X conditions.
```{r, error=TRUE}
res_mcts <- ctSweepM(
  dat            = dat,
  outcome        = "Y",
  conditions     = c("X1", "X2", "X3"),
  sweep_vars     = c("X2", "X3"),
  sweep_range    = 6:9,
  thrY           = 7,
  thrX_default   = 7,
  dir.exp        = 1,
  return_details = TRUE
)

head(res_mcts$summary)
```

---

# OTS–QCA: Outcome Sweep (`otSweep`)

OTS–QCA varies only the threshold of **Y**, keeping X thresholds fixed.
```{r}
res_ots <- otSweep(
  dat            = dat,
  outcome        = "Y",
  conditions     = c("X1", "X2", "X3"),
  sweep_range    = 6:9,
  thrX           = c(X1 = 7, X2 = 7, X3 = 7),
  dir.exp        = 1,
  return_details = TRUE
)

head(res_ots$summary)
```

---

# DTS–QCA: Two-Dimensional Sweep (`dtSweep`)

DTS–QCA varies both **X thresholds** and **Y thresholds**, creating a full 2D grid.
```{r}
sweep_list_dts_X <- list(
  X1 = 6:8,
  X2 = 6:8,
  X3 = 6:8
)

sweep_range_dts_Y <- 6:8

res_dts <- dtSweep(
  dat            = dat,
  outcome        = "Y",
  conditions     = c("X1", "X2", "X3"),
  sweep_list_X   = sweep_list_dts_X,
  sweep_range_Y  = sweep_range_dts_Y,
  dir.exp        = 1,
  return_details = TRUE
)

head(res_dts$summary)
```

---

# Understanding the Output

Each sweep result contains:

- threshold values tested,
- minimized solution expression,
- solution consistency (`inclS`),
- solution coverage (`covS`).

General guidance:

- **Consistency ≥ 0.8** is typically required for sufficiency.
- **Coverage** indicates empirical relevance; higher is better.
- A solution sensitive to small threshold changes suggests low robustness.

---

# Handling Multiple Solutions (New in v0.2.0)

## Why Multiple Solutions Matter

When QCA minimization produces multiple equivalent intermediate solutions, researchers face a methodological challenge: which solution should be reported? Traditional approaches often report only the first solution (M1), but this may miss important causal heterogeneity.

TSQCA v0.2.0 addresses this by:

1. **Detecting** when multiple solutions exist
2. **Extracting** core conditions common to all solutions
3. **Identifying** peripheral and unique terms

## Core vs. Peripheral Conditions

Understanding the distinction between core and peripheral conditions is essential for robust QCA interpretation:

| Type | Definition | Interpretation |
|------|------------|----------------|
| **Core conditions** | Present in ALL solutions | Robust findings; essential causal factors |
| **Peripheral conditions** | Present in SOME but not all solutions | Context-dependent; may vary across cases |
| **Unique terms** | Present in only ONE specific solution | Solution-specific; least robust |

## Using `extract_mode`

The `extract_mode` parameter controls how solutions are extracted:

### Mode: "first" (Default)
```{r, eval=FALSE}
# Returns only the first solution (M1)
# Backward compatible with v0.1.x
result <- otSweep(
  dat = dat,
  outcome = "Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 6:9,
  thrX = c(X1 = 7, X2 = 7, X3 = 7),
  extract_mode = "first"  # Default
)
```

### Mode: "all"
```{r, eval=FALSE}
# Returns all solutions concatenated
# Useful for seeing all equivalent solutions
result_all <- otSweep(
  dat = dat,
  outcome = "Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 6:9,
  thrX = c(X1 = 7, X2 = 7, X3 = 7),
  extract_mode = "all"
)

# Output includes n_solutions column
head(result_all$summary)
# expression column shows: "M1: A*B + C; M2: A*B + D; M3: ..."
```

### Mode: "core"
```{r, eval=FALSE}
# Returns core conditions common to all solutions
# Best for identifying robust findings
result_core <- otSweep(
  dat = dat,
  outcome = "Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 6:9,
  thrX = c(X1 = 7, X2 = 7, X3 = 7),
  extract_mode = "core"
)

# Output includes:
# - expression: core conditions
# - peripheral_terms: conditions in some but not all solutions
# - unique_terms: solution-specific conditions
# - n_solutions: number of equivalent solutions
```

## Practical Example

Consider a scenario where QCA produces three equivalent solutions:

- M1: `A*B + C → Y`
- M2: `A*B + D → Y`
- M3: `A*B + E → Y`

The analysis reveals:

| Component | Terms | Interpretation |
|-----------|-------|----------------|
| Core | `A*B` | Present in all three solutions; robust finding |
| Peripheral | `C, D, E` | Each appears in one solution; context-dependent |
| Unique (M1) | `C` | Only in solution 1 |
| Unique (M2) | `D` | Only in solution 2 |
| Unique (M3) | `E` | Only in solution 3 |

**Recommendation**: Report the core conditions (`A*B → Y`) as your main finding, and discuss the peripheral conditions as alternative pathways in your discussion section.

---

# Generating Reports (New in v0.2.0)

## Overview

The `generate_report()` function creates comprehensive markdown reports from your analysis results. This automates the documentation process and ensures reproducibility.

## Report Formats

### Full Report

Contains comprehensive analysis details:

- Analysis settings (for reproducibility)
- Summary table across all thresholds
- Per-threshold detailed results
- All solution formulas
- Core and peripheral conditions
- Fit measures (consistency, coverage, PRI)

```{r, eval=FALSE}
# Generate full report
generate_report(res_ots, "my_analysis_full.md", format = "full")
```

### Simple Report

Designed for journal manuscripts:

- Condensed format
- Essential information only
- Ready for supplementary materials

```{r, eval=FALSE}
# Generate simple report
generate_report(res_ots, "my_analysis_simple.md", format = "simple")
```

## Using Reports Effectively

### For Research Papers

1. Run analysis with `return_details = TRUE` (default in v0.2.0)
2. Generate a **simple report** for the main manuscript
3. Generate a **full report** for supplementary materials

```{r, eval=FALSE}
# Complete workflow
result <- otSweep(
  dat = mydata,
  outcome = "Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 6:9,
  thrX = c(X1 = 7, X2 = 7, X3 = 7)
)

# For main text
generate_report(result, "manuscript_results.md", format = "simple")

# For supplementary materials
generate_report(result, "supplementary_full.md", format = "full")
```

### Accessing Analysis Parameters

All analysis parameters are stored in `result$params` for reproducibility:

```{r, eval=FALSE}
# View stored parameters
result$params

# Includes:
# - outcome, conditions: variable names
# - thrX, thrY: threshold values
# - incl.cut, n.cut, pri.cut: QCA parameters
# - dir.exp, include: minimization settings
```

---

# Best Practices

## Start Small, Then Expand

When using sweep functions, the number of QCA analyses grows quickly. A systematic approach prevents wasted computation:

### Step 1: Single Value Test
```{r, eval=FALSE}
# Test with a single threshold first
result <- otSweep(
  dat = dat,
  outcome = "Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 7,  # Single value
  thrX = c(X1 = 7, X2 = 7, X3 = 7)
)
```

### Step 2: Small Range
```{r, eval=FALSE}
# Expand to a small range
result <- otSweep(
  dat = dat,
  outcome = "Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 6:7,  # Small range
  thrX = c(X1 = 7, X2 = 7, X3 = 7)
)
```

### Step 3: Full Analysis
```{r, eval=FALSE}
# Run full analysis only after confirming it works
result <- otSweep(
  dat = dat,
  outcome = "Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 5:9,  # Full range
  thrX = c(X1 = 7, X2 = 7, X3 = 7)
)
```

## Computational Complexity

Understanding computational complexity helps plan your analysis:

| Function | Complexity | Example | Analyses |
|----------|------------|---------|----------|
| `otSweep()` | O(n) | 5 Y thresholds | 5 |
| `ctSweepS()` | O(n) | 5 X thresholds | 5 |
| `ctSweepM()` | O(m^k) | 3 thresholds × 3 conditions | 27 |
| `dtSweep()` | O(n × m^k) | 3 Y × 3^3 X | 81 |

### Managing Large Sweeps

For `dtSweep()` and `ctSweepM()`, reduce conditions first:

```{r, eval=FALSE}
# Manageable: 2 × 2 × 2 = 8 combinations
sweep_list <- list(X1 = 6:7, X2 = 6:7, X3 = 6:7)

# Caution: 5 × 5 × 5 = 125 combinations
sweep_list <- list(X1 = 5:9, X2 = 5:9, X3 = 5:9)

# Avoid: 5 × 5 × 5 × 5 × 5 = 3125 combinations!
sweep_list <- list(X1 = 5:9, X2 = 5:9, X3 = 5:9, X4 = 5:9, X5 = 5:9)
```

## Interpreting Results

### When Solutions Are Stable

If the same solution appears across multiple thresholds, your findings are robust:

```
thrY | expression    | inclS | covS
-----|---------------|-------|------
6    | A*B + C → Y   | 0.85  | 0.72
7    | A*B + C → Y   | 0.88  | 0.68
8    | A*B + C → Y   | 0.91  | 0.65
```

**Interpretation**: The solution `A*B + C` is robust across threshold variations.

### When Solutions Change

If solutions vary significantly, investigate the threshold sensitivity:

```
thrY | expression    | inclS | covS
-----|---------------|-------|------
6    | A*B + C → Y   | 0.82  | 0.75
7    | A*B → Y       | 0.89  | 0.62
8    | B*D → Y       | 0.93  | 0.45
```

**Interpretation**: Results are threshold-sensitive. Consider reporting the most theoretically justified threshold with appropriate caveats.

---

# Negated Outcome Analysis (New in v0.3.0)

## Why Analyze Negated Outcomes?

In QCA, researchers typically analyze conditions sufficient for the **presence** of an outcome (Y = 1). However, understanding conditions for the **absence** of an outcome (~Y) can provide equally valuable insights:

- What conditions lead to project **failure** (not success)?
- What factors contribute to customer **dissatisfaction** (not satisfaction)?
- What explains policy **non-adoption** (not adoption)?

## Using the `~` Notation

TSQCA v0.3.0 supports the QCA package's tilde (`~`) notation for negated outcomes:

```{r, eval=FALSE}
# Analyze conditions for Y >= threshold (standard)
result_Y <- otSweep(
  dat = dat,
  outcome = "Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 6:8,
  thrX = c(X1 = 7, X2 = 7, X3 = 7)
)

# Analyze conditions for Y < threshold (negated)
result_negY <- otSweep(
  dat = dat,
  outcome = "~Y",
  conditions = c("X1", "X2", "X3"),
  sweep_range = 6:8,
  thrX = c(X1 = 7, X2 = 7, X3 = 7)
)
```

## Interpreting Negated Results

When using `~Y`, the solution shows conditions sufficient for the **absence** of the outcome:

| Analysis | Solution Example | Interpretation |
|----------|------------------|----------------|
| `outcome = "Y"` | `X1*X2 + X3` | High X1 AND X2, OR high X3 → High Y |
| `outcome = "~Y"` | `~X1*~X3 + ~X2*~X3` | Low X1 AND X3, OR low X2 AND X3 → Low Y |

**Note**: Negated conditions (`~X1`) in the solution mean the **absence** of that condition (below threshold).

## All Sweep Functions Support Negation

```{r, eval=FALSE}
# ctSweepS with negated outcome
result <- ctSweepS(
  dat = dat,
  outcome = "~Y",
  conditions = c("X1", "X2", "X3"),
  sweep_var = "X3",
  sweep_range = 6:8,
  thrY = 7,
  thrX_default = 7
)

# ctSweepM with negated outcome
result <- ctSweepM(
  dat = dat,
  outcome = "~Y",
  conditions = c("X1", "X2"),
  sweep_list = list(X1 = 6:7, X2 = 6:7),
  thrY = 7
)

# dtSweep with negated outcome
result <- dtSweep(
  dat = dat,
  outcome = "~Y",
  conditions = c("X1", "X2"),
  sweep_list_X = list(X1 = 6:7, X2 = 7),
  sweep_range_Y = 6:8
)
```

## Checking Negation in Results

The `params` object stores whether negation was used:

```{r, eval=FALSE}
result <- otSweep(dat = dat, outcome = "~Y", ...)

# Check if negated
result$params$negate_outcome
# [1] TRUE

result$params$outcome
# [1] "~Y"
```

---

# Conclusion

TSQCA provides a structured and reproducible way to evaluate  
how threshold choices influence QCA results.

Using CTS, MCTS, OTS, and DTS sweeps, researchers can:

- assess robustness,
- identify stable causal patterns,
- detect threshold-sensitive relationships,
- and strengthen QCA validity.

**New in v0.3.0:**

- QCA-compatible argument names (`outcome`, `conditions`)
- Negated outcome support (`~Y` notation)
- Backward compatibility with deprecation warnings

**New in v0.2.0:**

- Detect and analyze multiple equivalent solutions
- Extract core conditions for robust findings
- Generate comprehensive reports automatically
- Access stored parameters for reproducibility


## References

For more information on TS-QCA methodology, see:

- Ragin, C. C. (2008). *Redesigning Social Inquiry: Fuzzy Sets and Beyond*. University of Chicago Press. DOI: [10.7208/chicago/9780226702797.001.0001](https://doi.org/10.7208/chicago/9780226702797.001.0001)
- Duşa, A. (2019). *QCA with R: A Comprehensive Resource*. Springer. DOI: [10.1007/978-3-319-75668-4](https://doi.org/10.1007/978-3-319-75668-4)
- Oana, I.-E., & Schneider, C. Q. (2024). A Robustness Test Protocol for Applied QCA: Theory and R Software Application. *Sociological Methods & Research*, 53(1), 57–88. DOI: [10.1177/00491241211036158](https://doi.org/10.1177/00491241211036158)



# Session Info
```{r}
sessionInfo()
```
